The parameter \Verb+calculation_mode+ needs to be set to
\Verb+event_based_risk+ in order to use this calculator.

Most of the job configuration parameters required for running a stochastic
event based risk calculation are the same as those described in the previous
sections for the scenario risk calculator and the classical probabilistic risk
calculator. The remaining parameters specific to the stochastic event based
risk calculator are illustrated through the example below.


\paragraph{Example 1}

This example illustrates a stochastic event based risk calculation which uses
a single configuration file to first compute the \glspl{acr:ses} and
\glspl{acr:gmf} for the given source model and ground motion model, and then
calculate event loss tables, loss exceedance curves and probabilistic
loss maps for structural losses, nonstructural losses and occupants,
based on the \glspl{acr:gmf}. The job configuration file required for
running this stochastic event based risk calculation is shown in
Listing~\ref{lst:config_event_based_risk_combined}.

\begin{listing}[htbp]
  \inputminted[firstline=1,firstnumber=1,fontsize=\scriptsize
  ,frame=single,bgcolor=lightgray,linenos,label=job.ini]{ini}{oqum/risk/verbatim/config_event_based_risk_combined.ini}
  \caption{Example combined configuration file for running a stochastic event based risk calculation (\href{https://raw.githubusercontent.com/gem/oq-engine/master/doc/manual/oqum/risk/verbatim/config_event_based_risk_combined.ini}{Download example})}
  \label{lst:config_event_based_risk_combined}
\end{listing}

Similar to that the procedure described for the Scenario Risk calculator, a
Monte Carlo sampling process is also employed in this calculator to take into
account the uncertainty in the conditional loss ratio at a particular
intensity level. Hence, the parameters \Verb+asset_correlation+ and
\Verb+master_seed+ may be defined as previously described for the Scenario
Risk calculator in Section~\ref{sec:config_scenario_risk}. The parameter
``risk\_investigation\_time'' specifies the time period for which the event
loss tables and loss exceedance curves will be calculated, similar to the
Classical Probabilistic Risk calculator. If this parameter is not provided in
the risk job configuration file, the time period used is the same as that
specifed in the hazard calculation using the parameter ``investigation\_time''.

The new parameters introduced in this example are described below:

\begin{itemize}

  \item \Verb+minimum_intensity+: this optional parameter specifies the minimum
    intensity levels for each of the intensity measure types in the risk model.
    Ground motion fields where each ground motion value is less than the 
    specified minimum threshold are discarded. This helps speed up calculations
    and reduce memory consumption by considering only those ground motion fields
    that are likely to contribute to losses. It is also possible to set the same
    threshold value for all intensity measure types by simply providing a single
    value to this parameter. For instance: ``minimum\_intensity = 0.05'' would
    set the threshold to 0.05 g for all intensity measure types in the risk 
    calculation.
    If this parameter is not set, the \glsdesc{acr:oqe} extracts the minimum
    thresholds for each intensity measure type from the vulnerability
    models provided, picking the lowest intensity value for which a mean loss
    ratio is provided.

  \item \Verb+return_periods+: this parameter specifies the list of return
    periods (in years) for computing the aggregate loss curve.
    If this parameter is not set, the \glsdesc{acr:oqe} uses a default set of
    return periods for computing the loss curves. The default return periods
    used are from the list: [5, 10, 25, 50, 100, 250, 500, 1000, ...], with 
    its upper bound limited by \Verb+(ses_per_logic_tree_path × investigation_time)+

  \item \Verb+avg_losses+: this boolean parameter specifies whether the average
    asset losses over the time period ``risk\_investigation\_time'' should be
    computed. The default value of this parameter is \Verb+true+.

    \begin{equation*}
    \begin{split}
    average\_loss & = sum(event\_losses) \\
                 & \div (hazard\_investigation\_time \times ses\_per\_logic\_tree\_path) \\
                 & \times risk\_investigation\_time
    \end{split}
    \end{equation*}

\end{itemize}

The above calculation can be run using the command line:

\begin{minted}[fontsize=\footnotesize,frame=single,bgcolor=lightgray]{shell-session}
user@ubuntu:~\$ oq engine --run job.ini
\end{minted}

Computation of the loss tables, loss curves, and average losses for each
individual \gls{asset} in the \gls{exposuremodel} can be resource intensive,
and thus these outputs are not generated by default, unless instructed to by
using the parameters described above.


Users may also begin an event based risk calculation by providing a precomputed
set of \glspl{acr:gmf} to the \gls{acr:oqe}. The following example describes the
procedure for this approach.


\paragraph{Example 2}

This example illustrates a stochastic event based risk calculation which uses
a file listing a precomputed set of \glspl{acr:gmf}. These \glspl{acr:gmf} can
be computed using the \glsdesc{acr:oqe} or some other software. The
\glspl{acr:gmf} must be provided in either the \gls{acr:nrml} schema or the
csv format as presented in Section~\ref{subsec:output_event_based_psha}.
Listing~\ref{lst:output_gmf_xml} shows an example of a \glspl{acr:gmf} file in
the \gls{acr:nrml} schema and Table~\ref{output:gmf_event_based} shows an
example of a \glspl{acr:gmf} file in the csv format. If the \glspl{acr:gmf}
file is provided in the csv format, an additional csv file listing the site
ids must be provided using the parameter \Verb+sites_csv+. See
Table~\ref{output:sitemesh} for an example of the sites csv file, which
provides the association between the site ids in the \glspl{acr:gmf} csv file
with their latitude and longitude coordinates.

Starting from the input \glspl{acr:gmf}, the \gls{acr:oqe} can calculate event
loss tables, loss exceedance curves and probabilistic loss maps for structural
losses, nonstructural losses and occupants. The
job configuration file required for running this stochastic event based risk
calculation starting from a precomputed set of \glspl{acr:gmf} is shown in
Listing~\ref{lst:config_gmf_event_based_risk}.

\begin{listing}[htbp]
  \inputminted[firstline=1,firstnumber=1,fontsize=\scriptsize
  ,frame=single,bgcolor=lightgray,linenos,label=job.ini]{ini}{oqum/risk/verbatim/config_gmf_event_based_risk.ini}
  \caption{Example combined configuration file for running a stochastic event based risk calculation starting from a precomputed set of ground motion fields (\href{https://raw.githubusercontent.com/gem/oq-engine/master/doc/manual/oqum/risk/verbatim/config_gmf_event_based_risk.ini}{Download example})}
  \label{lst:config_gmf_event_based_risk}
\end{listing}


\paragraph{Additional parameters}

A few additional parameters related to the event based risk calculator that
may be useful for controlling specific aspects of the calculation are listed
below:

\begin{itemize}

  \item \Verb+individual_curves+: this boolean parameter is used to specify if
    the asset loss curves for each branch realization should be saved to the 
    datastore. For the asset loss curves output, by default the engine only 
    saves and exports statistical results, i.e. the mean and quantile asset 
    loss curves. If you want the asset loss curves for each of the individual 
    branch realizations, you must set \Verb+individual_curves=true+ in the job 
    file. Please take care: if you have hundreds of realizations, the data 
    transfer and disk space requirements will be orders of magnitude larger 
    than just returning the mean and quantile asset loss curves, and the 
    calculation might fail. The default value of \Verb+individual_curves+ is 
    \Verb+false+.

  \item \Verb+asset_correlation+: if the uncertainty in the loss ratios
    has been defined within the \gls{vulnerabilitymodel}, users can specify
    a coefficient of correlation that will be used in the Monte Carlo sampling
    process of the loss ratios, between the assets that share the same
    \gls{taxonomy}. If the \Verb+asset_correlation+ is set to one,
    the loss ratio residuals will be perfectly correlated. On the other hand,
    if this parameter is set to zero, the loss ratios will be sampled
    independently. If this parameter is not defined, the
    \glsdesc{acr:oqe} will assume zero correlation in the vulnerability. As of
    \glsdesc{acr:oqe18}, \Verb+asset_correlation+ applies only to continuous
    \glspl{vulnerabilityfunction} using the lognormal or Beta distribution; 
    it does not apply to \glspl{vulnerabilityfunction} defined using the PMF
    distribution. Although partial correlation was supported in previous
    versions of the engine, beginning from \glsdesc{acr:oqe22}, values between
    zero and one are no longer supported due to performance considerations. The
    only two values permitted are \Verb+asset_correlation = 0+ and 
    \Verb+asset_correlation = 1+.

  \item \Verb+ignore_covs+: this parameter controls the propagation of 
    vulnerability uncertainty to losses. The vulnerability functions using 
    continuous distributions (such as the lognormal distribution or beta 
    distribution) to characterize the uncertainty in the loss ratio 
    conditional on the shaking intensity level, specify the mean loss ratios 
    and the corresponding coefficients of variation for a set of intensity 
    levels. They are used to build the so called epsilon matrix within the 
    engine, which is how loss ratios are sampled from the distribution for 
    each asset. There is clearly a performance penalty associated with the 
    propagation of uncertainty in the vulnerability to losses. The epsilon 
    matrix has to be computed and stored, and then the worker processes have 
    to read it, which involves large quantities of data transfer and memory 
    usage. Setting \Verb+ignore_covs = true+ in the job file will result in 
    the engine using just the mean loss ratio conditioned on the shaking 
    intensity and ignoring the uncertainty. This tradeoff of not propagating 
    the vulnerabilty uncertainty to the loss estimates can lead to a 
    significant boost in performance and tractability. The default value of 
    \Verb+ignore_covs+ is \Verb+false+. 

\end{itemize}
