The Scenario Risk Calculator produces the following set of output files:

\begin{enumerate}

  \item \Verb+agglosses+: this file contains the aggregated scenario
    loss statistics for the entire portfolio of \glspl{asset} defined
    in the \gls{exposuremodel}. The mean (\Verb+mean+) and standard
    deviation (\Verb+stddev+) of the total loss for the portfolio of
    \glspl{asset} are listed in this file.

  \item \Verb+losses_by_taxon+: this file contains the scenario
    loss statistics for each of the \glspl{taxonomy} defined in the
    \gls{exposuremodel}. For each \gls{taxonomy}, the mean (\Verb+mean+)
    and associated standard deviation (\Verb+stddev+)
    of the losses for each taxonomy are listed in this file.

  \item \Verb+losses_by_asset+: this file contains mean (\Verb+mean+) and
    associated standard deviation (\Verb+stddev+) of the scenario loss for all
    \glspl{asset} at each of the unique locations in the \gls{exposuremodel}.

  \item \Verb+losses_by_event+: this file contains the total loss for the
    portfolio of \glspl{asset} defined in the \gls{exposuremodel} for each
    realization of the scenario generated in the Monte Carlo simulation process.


\end{enumerate}

If the calculation involves multiple \glspl{acr:gmpe}, separate output files
are generated for each of the above outputs, for each of the different
\glspl{acr:gmpe} used in the calculation.

These different output files for Scenario Risk calculations are described in
more detail in the following subsections.


\subsection{Scenario loss statistics}
\label{subsec:scenario_loss_statistics}

\subsubsection{Asset loss statistics}
\label{subsubsec:scenario_asset_loss_statistics}

This output is always produced for a Scenario Risk calculation and comprises a
mean total loss and associated standard deviation for each of the individual
\glspl{asset} defined in the \gls{exposuremodel} that fall within the
\Verb+region_constraint+ and have a computed \gls{acr:gmf} value available
within the defined \Verb+asset_hazard_distance+. These results are stored in a
comma separate value (.csv) file as illustrated in the example shown in
Table~\ref{output:scenario_loss_asset}.

\input{oqum/risk/verbatim/output_scenario_loss_asset}


\subsubsection{Taxonomy loss statistics}
\label{subsubsec:scenario_taxonomy_loss_statistics}

The Scenario Risk calculator also estimates the total expected losses for
assets of each \gls{taxonomy}. This distribution of losses per building
\gls{taxonomy} is depicted in the example output file snippet in
Table~\ref{output:scenario_loss_taxonomy}.

\input{oqum/risk/verbatim/output_scenario_loss_taxonomy}

The output file lists the mean loss aggregated for each building typology
found in the exposure model for all loss types (amongst ``structural'',
``nonstructural'', ``contents'', or ``business\_interruption'') for which a
\gls{vulnerabilitymodel} file was provided in the configuration file.


\subsubsection{Total loss statistics}
\label{subsubsec:scenario_total_loss_statistics}

This output is always produced for a Scenario Risk calculation and comprises a
mean total loss and associated standard deviation for the selected earthquake
rupture. These results are stored in a comma separate value (.csv) file as
illustrated in the example shown in Table~\ref{output:scenario_loss_total}.

\input{oqum/risk/verbatim/output_scenario_loss_total}

The important attributes in a scenario total loss statistics output file are
described below:


\begin{itemize}

  \item \Verb+LossType+: the type of losses that are being stored. This
    parameter is taken from the \gls{vulnerabilitymodel} that was used in the
    loss calculations (e.g. fatalities, economic loss).

  \item \Verb+Unit+: this attribute defines the units in which the losses are
    being measured (e.g. USD or EUR). These units are the same as those defined
    in the \gls{exposuremodel} used for the calculation.

  \item \Verb+Mean+: the mean total loss across the portfolio of assets for the
    selected earthquake rupture.

  \item \Verb+Standard Deviation+: the standard deviation of the total loss 
    across the portfolio of assets for the selected earthquake rupture.

\end{itemize} 